Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-10 WSSSPE1_report/WSSSPE1_summary_report.tex
Added Contact details for James Howison.
Added non-breaking spaces in author names to avoid line breaks between first and last names.

\author{Daniel S. Katz$^{(1)}$, Hilmar Lapp$^{(2)}$, Ketan Maheshwari$^{(3)}$, Frank L\"{o}ffler$^{(4)}$, Matthew Turk$^{(5)}$, Marcus D. Hanwell$^{(6)}$, Nancy Wilkins-Diehr$^{(7)}$, James Hetherington$^{(8)}$, James Howison$^{(9)}$, Sou-Cheng T. Choi$^{(10)}$, Shel Swenson$^{(11)}$,  Bruce Berriman$^{(12)}$, Andy R. Terrel$^{(13)}$, Colin Venters$^{(14)}$}
\note{Authors, please add/check middle initials and affiliations.}

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(3)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(4)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(5)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(8)}$ Leader, Research Software Development Team, University College London; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(9)}$ xxx}
%
\thanks{{}$^{(10)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA; (\url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

>>>>

\author{Daniel~S.~Katz$^{(1)}$, Hilmar~Lapp$^{(2)}$, Ketan~Maheshwari$^{(3)}$, Frank~L\"{o}ffler$^{(4)}$, Matthew~Turk$^{(5)}$, Marcus~D.~Hanwell$^{(6)}$, Nancy~Wilkins-Diehr$^{(7)}$, James~Hetherington$^{(8)}$, James~Howison$^{(9)}$, Sou-Cheng~T.~Choi$^{(10)}$, Shel~Swenson$^{(11)}$,  Bruce~Berriman$^{(12)}$, Andy~R.~Terrel$^{(13)}$, Colin~Venters$^{(14)}$}
\note{Authors, please add/check middle initials and affiliations.}

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(3)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(4)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(5)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(8)}$ Leader, Research Software Development Team, University College London; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(9)}$ University of Texas at Austin; \url{jhowison@ischool.utexas.edu}}
%
\thanks{{}$^{(10)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA; (\url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}
